In this study, we proposed a Word Similarity-based Spectral Clustering (WSbSC) method for Bengali extractive text summarization which can also be used in other low resource languages. the proposed method used geometric mean of Gaussian similarities between individual word pairs to identify deeper semantic relationship within two sentences. This method for calculating sentence similarity helps WSbSC to significantly outperform other recent graph based extractive text summarization methods on four varying datasets with different sizes and sources. This improvement in performance is also helped by the use of spectral clustering which helps to improve coherence and relevance of the generated summaries by minimizing redundancy and maximizing topic coverage. High performance across three ROUGE metrics on four datasets prove the versatility and robustness of the proposed method. WSbSC can also be extended into other languages as shown through our experimentations on Hindi, Marathi and Turkish languages proving the generalizability of the method. This method addresses the need for an effective summarization technique in Bengali language as Bengali remains under-represented in NLP research despite it being the 7th largest language in the world.\\

Through results of extensive experimentations, we showed the strengths of the proposed WSbSC method as it outperforms several baseline techniques using a better approach to grouping sentences into key topics. Despite these promising results, there are areas with limitation that requires further improvement. WSbSC may face limitations on highly specialized or domain-specific texts, where deeper linguistic features beyond word similarity could be considered. The lack of consideration for word order in a sentence is also a key limitation which could be explored in the future. Future works could also explore hybrid models that integrate modern post-processing techniques to improve the flow of the output.\\

In conclusion, this work contributes to the growing body of computational linguistics research focused on low-resource languages like Bengali. The WSbSC method offers a novel approach for extractive summarization by using a new algorithm for calculating similarity between two sentences and sets the stage for further advancements in both Bengali text processing and multilingual summarization techniques.
