% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{graphicx} % Required for inserting images
\usepackage{xcolor,colortbl}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage[english]{babel}
\input{helping_files/bangla_commands}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage[numbers]{natbib}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.7}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}



\title{Extractive Text Summarization Using Word Similarity Based Spectral Clustering}
\author{Fahim Morshed, Md. Abdur Rahman, Sumon Ahmed}


% Document
\begin{document}

    \maketitle
    \setlength{\parindent}{0pt}
    \begin{abstract}
        Extractive Text Summarization is the process of picking the best parts of
        a larger text without losing any key information.
        This is really necessary in this day and age to get concise information
        faster due to digital information overflow.
        But research in this field, specially in Bengali, has been inadequate.
        This papers objective is to develop an extractive text summarization
        method for Bengali language, that uses the latest NLP techniques
        and can be extended to other low resource languages.
        We developed a word Similarity-based Spectral Clustering (WSbSC) method
        for Bengali extractive text summarization.
        It extracts key sentences by grouping semantically similar sentences into clusters
        with a novel sentence similarity calculating algorithm.
        We took the geometric means of individual Gaussian similarity of Word embedding vectors.
        Then used TF-IDF ranking to pick the best sentence from each cluster.
        We tested this method on four different Bengali text summarization datasets,
        and it outperformed other recent models on every ROUGE metric on average by 43.2\%.
        We also experimented the method on Turkish, Marathi and Hindi language and found that the
        performance on those languages often exceeded the performance of Bengali.
        We also provide a new high quality dataset for text summarization evaluation.
        We believe this research is a crucial addition to Bengali Natural Language Processing,
        that can easily be extended into other languages.
    \end{abstract}

    \section{Introduction}\label{sec:introduction}
    \input{chapters/1_introduction}

    \section{Literature Review}\label{sec:literature-review}
    \input{chapters/2_literature-review}

    \section{Methodology}\label{sec:methodology}
    \input{chapters/3_methodology}

    \section{Result}\label{sec:result}
    \input{chapters/4_result}

    \section{Discussion}\label{sec:discussion}
    \input{chapters/5_discussion}

    \section{Conclusion}\label{sec:conclusion}
    \input{chapters/6_Conclusion}


    \bibliography{bib/main}
    \bibliographystyle{plainnat}



\end{document}
